Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 testbed.tex
Updating cross compiling

% Get the files
\begin{lstlisting}[]
$ wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
\end{lstlisting}
\FloatBarrier

@@

\item Download the \ac{Raspi} toolchain for 64-bit Linux from: \\
\texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
\texttt{\$HOME} directory. \\

\item Extract the downloaded file locally in the NFS server. After
this operation, there should be a new directory for the toolchain
in the server. \\

\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
Linux environment variable of the server. This will help the server OS
to recognize the location of the compiler command, which will be needed
later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
\texttt{\$HOME/.profile}. \\

\item Restart the server session in order for the changes made in the
previous step take effect. To verify this, open a new terminal and type:
\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
should return an output similar to:

\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
Copyright (C) 2014 Free Software Foundation, Inc.
This is free software; see the source for copying conditions.  There is NO
warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\

>>>>

% Get the files
\begin{lstlisting}[]
$ wget http://kom.aau.dk/project/TuneSCode/raspi/rasp_config.zip
# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
\end{lstlisting}
\FloatBarrier

@@

\item Create toolchain directory:
\begin{lstlisting}[]
$ TOOLCHAINDIR="${HOME}/toolchains"
$ mkdir -p $TOOLCHAINDIR
$ cd $TOOLCHAINDIR
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Download the \ac{Raspi} toolchain for 64-bit Linux from.
A more recent \ac{Raspi} toolchain may be available at
\texttt{http://buildbot.steinwurf.dk/toolchains/linux/}:

\begin{lstlisting}[]
$ TOOLCHAIN="raspberry-gxx49-arm"
$ wget http://kom.aau.dk/project/TuneSCode/raspi/${TOOLCHAIN}.zip
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Extract the downloaded file:
%locally in the NFS server. After
%this operation, there should be a new directory for the toolchain
%in the server. \\
\begin{lstlisting}[]
$ unzip ${TOOLCHAIN}.zip
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item (Optional) Delete zip file:
%locally in the NFS server. After
%this operation, there should be a new directory for the toolchain
%in the server. \\
\begin{lstlisting}[]
$ rm ${TOOLCHAIN}.zip
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item We can now verify that the ARM cross compiler is working:

\begin{lstlisting}[]
$ ${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++ --version
raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
Copyright (C) 2014 Free Software Foundation, Inc.
This is free software; see the source for copying conditions.  There is NO
warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

%\begin{lstlisting}[]
%$ echo "${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++"
%/home/<USER>/toolchains/raspberry-gxx49-arm/bin/raspberry-gxx49-arm-g++
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}

%    The ARM cross compilers should now be located in

\item Make toolchain binaries available systemwide. Instead of calling
the ARM cross compiler using its full path, we can make it accessible
from the command shell systemwide. One way to do this is by adding the 
toolchain binaries directory to the Linux environment variable \texttt{PATH}
when the \ac{OS} starts up:

%\item Add toolchain binaries to \texttt{PATH}. Instead specifying the full
%path to the toolchain binaries we can instead tell the operation system
%where to search for it. This makes the toolchain binaries available
%systemwide.

\begin{lstlisting}[]
$ echo PATH=\"\$PATH:${TOOLCHAINDIR}/${TOOLCHAIN}/bin\" >> ${HOME}/.profile
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
%$ printf 'PATH="%s/%s/bin"\n' "${TOOLCHAINDIR}" "${TOOLCHAIN}" >> ${HOME}/.profile

%\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
%Linux environment variable of the server. This will help the server OS
%to recognize the location of the compiler command, which will be needed
%later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
%\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
%\texttt{\$HOME/.profile}. \\

\texttt{~/.profile} should now contain the line we inserted. There may be more
code in you file.
% MAC and Hostname file
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$HOME/.profile}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
PATH="$PATH:/home/<USERNAME>/toolchains/raspberry-gxx49-arm/bin"
\end{lstlisting}
\FloatBarrier

\item Update \texttt{PATH}. Source \texttt{~/.profile} to make the changes
take effect in your system:
\begin{lstlisting}[]
$ source ${HOME}/.profile
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item ARM cross compiler should now be available systemwide:

\begin{lstlisting}[]
$ raspberry-gxx49-arm-g++ --version
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

%\item Restart the server session in order for the changes made in the
%previous step take effect. To verify this, open a new terminal and type:
%\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
%should return an output similar to:
%
%\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
%Copyright (C) 2014 Free Software Foundation, Inc.
%This is free software; see the source for copying conditions.  There is NO
%warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
